Weakly informative observations: not the winner

### 2025-03-05 inst/notthewinner.Rmd
use new-style suppfun()

```{r}
(H <- 
	rank_likelihood(c(a=3,c=2,b=1,d=4)) + 
	rank_likelihood(c(b=2,c=3,d=1    )) + 
	rank_likelihood(c(d=2,a=3,c=1    )) + 
	rank_likelihood(c(b=1,d=2        )) )
```

@@

```{r,uninformativesupportfunction}
library("partitions")
H # as before, here for convenience
M <- perms(5)   # uninformative!
SL <- list()
for(i in seq_len(ncol(M))){
	jj <- M[,i,drop=TRUE]
	names(jj) <- letters[seq_along(jj)]
	SL[[i]] <- H + rank_likelihood(jj)
}
SL <- as.suplist(SL)
```

>>>>

```{r}
(H <- 
	suppfun(c(a=3,c=2,b=1,d=4)) + 
	suppfun(c(b=2,c=3,d=1    )) + 
	suppfun(c(d=2,a=3,c=1    )) + 
	suppfun(c(b=1,d=2        )) )
```

@@

```{r,uninformativesupportfunction}
library("partitions")
H # as before, here for convenience
M <- perms(5)   # uninformative!
SL <- list()
for(i in seq_len(ncol(M))){
	jj <- M[,i,drop=TRUE]
	names(jj) <- letters[seq_along(jj)]
	SL[[i]] <- H + suppfun(jj)
}
SL <- as.suplist(SL)
```
